### 2025-01-02 paper/icml25/first/sects/introduction.tex
minors on intro

Learnign control policies has important applications in robotics \cite{Singh22}, autonomous driving \cite{Elallid22}, swarm intelligence \cite{Tang21} and many other fields. Recently, a reinforcement learning algorithm has gained popularity, SHAC\cite{Xu22}. SHAC is a simple and yet effective algorithm that exploits differentiable simulators to learn control policies effectively.

Despite its effectiveness, the main limitations of SHAC are two fold. Firstly, it requires a differentiable simulator and differentiable reward function to work properly. Both of which may be not feasible to obtain in practice, especially with inherently sparse rewards. Secondly, even when a differentiable simulator is available, SHAC has been shown to be sensitive to complex dynamics such as object collisions~\cite{Georgiev24}.

In this work, we aim to address both these limitation by approximating the gradients of the differentiable simulator. In particular, we will replace both the simulator and the reward function with a neural network trained in tandem with the policy network and value network. Overall, this will provide an algorithm that is more robust to complex dynamics, sparse rewards, and can work in a wider range of environments. On the other hand, however, this will also introduce additional complexity and computational cost tied to training additional networks.

We test our framework---dubbed \fname{}---against PPO\cite{Schulman17} and SHAC\cite{Xu22}, the former a state-of-the-art reinforcement learning algorithm for non-differentiable environments, and the latter, a state-of-the-art reinforcement learning algorithm for differentiable environments. We compare these algorithm on a set of environments with different numbers of agents. This allows us to evaluate the performance of these algorithm as the search space grows with the number of agents.

>>>>

Learnign control policies has important applications in robotics~\cite{Singh22}, autonomous driving~\cite{Elallid22}, swarm intelligence~\cite{Tang21} and many other fields. Recently, a reinforcement learning algorithm has gained popularity, SHAC~\cite{Xu22}. SHAC is a simple and yet effective algorithm that exploits differentiable simulators to learn control policies effectively.

Despite its effectiveness, the main limitations of SHAC are twofold. Firstly, it requires a differentiable simulator and differentiable reward function to work properly. Both of which may be not feasible to obtain in practice, especially with inherently sparse rewards. Secondly, even when a differentiable simulator is available, SHAC has been shown to be sensitive to complex dynamics such as object collisions~\cite{Georgiev24}.

In this work, we aim to address both these limitations by approximating the gradients of the differentiable simulator. In particular, we will replace both the simulator and the reward function with a neural network trained in tandem with the policy network and value network. Overall, this will provide an algorithm that is more robust to complex dynamics, sparse rewards, and can work in a wider range of environments. On the other hand, however, this will also introduce additional complexity and computational cost tied to training additional networks.

We evaluate our framework---dubbed \fname{}---against PPO~\cite{Schulman17}, a state-of-the-art algorithm for non-differentiable environments, and SHAC~\cite{Xu22}, designed for differentiable environments. We compare these algorithms on environments with varying numbers of agents, allowing us to assess their performance as the search space grows.
